How does increasing $s$ and $k$ effect log normalising constant estimation

### 2023-04-24 src/naomi-simple_increase-s-k/increase-s-k.Rmd
Rerun all PCA-AGHQ using no samples for lower memory, then rerun increase-s-k notebook

read_sk(s = 1, k = 3)
read_sk(s = 2, k = 3)
read_sk(s = 3, k = 3)
read_sk(s = 4, k = 3)
read_sk(s = 5, k = 3)

@@

k3 <- list(s1k3, s2k3, s3k3, s4k3, s5k3)
k3_lognormconsts <- sapply(k3, function(x) x$quad$normalized_posterior$lognormconst)
k3_times <- sapply(k3, function(x) x$time)

rm(list = c("k3", "s1k3", "s2k3", "s3k3", "s4k3", "s5k3"))
gc()

@@

```{r}
df <- data.frame(
  s = rep(1:5, times = 3),
  k = rep(c(2, 3, 5), each = 5),
  lognormconst = c(k2_lognormconsts, k3_lognormconsts, k5_lognormconsts),
  time = c(k2_times, k3_times, k5_times)
)

>>>>

read_sk(s = 1, k = 3)
read_sk(s = 2, k = 3)
read_sk(s = 3, k = 3)
read_sk(s = 4, k = 3)
read_sk(s = 5, k = 3)
read_sk(s = 7, k = 3)
read_sk(s = 8, k = 3)

@@

k3 <- list(s1k3, s2k3, s3k3, s4k3, s5k3, s7k3, s8k3)
k3_lognormconsts <- sapply(k3, function(x) x$quad$normalized_posterior$lognormconst)
k3_times <- sapply(k3, function(x) x$time)

rm(list = c("k3", "s1k3", "s2k3", "s3k3", "s4k3", "s5k3", "s7k3", "s8k3"))
gc()

@@

```{r}
df <- data.frame(
  s = c(1:5, 1:5, 7, 8, 1:5),
  k = rep(c(2, 3, 5), times = c(5, 7, 5)),
  lognormconst = c(k2_lognormconsts, k3_lognormconsts, k5_lognormconsts),
  time = c(k2_times, k3_times, k5_times)
)
